---
title: "Lin- cell metabolomics analysis"
author: "Jennifer Grants"
date: "8/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 6)
```

```{r warning = FALSE, message = FALSE}
library(tidyverse)
library(here)
library(broom)
library(ggsignif)
```

## 1) Lin- cell pellets harvested and prepared for GC/MS analysis by J. Grants (2018-06-28)
File path for prep documents: F:\Karsan Lab\Personal Folders\Jennifer G\miR-146a Metabolism project\Metabolomics analysis\2018-06-28 Lin-metab-1



## 2) Data acquired by UVic Proteomics
Original data files from UVic saved: F:\Karsan Lab\Personal Folders\Jennifer G\miR-146a Metabolism project\Metabolomics analysis\2018-06-28 Lin-metab-1\Results\Original report



```{r data, warning = FALSE}
glc <- read.csv("data/Glucose_metab.csv") %>% 
  separate(col = Sample_nmol.10.6.cells, into = c("Genotype", "x"), sep = "-") %>%
  select(-x) %>%
  gather(Metabolite, nmol_10Mcells, -Genotype)
FA <- read.csv("data/FA_metab.csv") %>% 
  separate(col = Sample_nmol.10.6.cells, into = c("Genotype", "x"), sep = "-") %>%
  select(-x) %>%
  gather(Metabolite, nmol_10Mcells, -Genotype)
TCA <- read.csv("data/TCA_metab.csv") %>% 
  separate(col = Sample_nmol.10.6.cells, into = c("Genotype", "x"), sep = "-") %>%
  select(-x) %>%
  gather(Metabolite, nmol_10Mcells, -Genotype)
other <- read.csv("data/Other_metab.csv") %>% 
  separate(col = Sample_nmol.10.6.cells, into = c("Genotype", "x"), sep = "-") %>%
  select(-x) %>%
  gather(Metabolite, nmol_10Mcells, -Genotype)
PO4 <- read.csv("data/PO4_metab.csv") %>% 
  separate(col = Sample_nmol.10.6.cells, into = c("Genotype", "x"), sep = "-") %>%
  select(-x) %>%
  gather(Metabolite, nmol_10Mcells, -Genotype)

```

## 3) Identify significant differences between WT vs. miR-146a KO, and WT vs. IL6/miR-146a DKO

### Glucose metabolism
```{r glc_initial_plots, fig.width = 10}
glc$Genotype <- factor(glc$Genotype, levels = c("WT", "KO", "IDKO"))

ggplot(glc, aes(Genotype, nmol_10Mcells)) +
  geom_boxplot(aes(fill = Genotype)) +
  facet_wrap(~Metabolite, nrow = 1) +
  labs(y = expression("nmol / 10"^"6"~"cells")) +
  scale_y_continuous(trans = "log10") +
  theme_classic(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_signif(comparisons = list(c("WT", "KO"), c("WT", "IDKO")), test = "t.test", map_signif_level = TRUE, step_increase = 0.1, tip_length = 0.01)
```

### TCA metabolism
```{r tca_initial_plots, fig.width = 12, fig.height = 12}
TCA$Genotype <- factor(TCA$Genotype, levels = c("WT", "KO", "IDKO"))

ggplot(TCA, aes(Genotype, nmol_10Mcells)) +
  geom_boxplot(aes(fill = Genotype)) +
  facet_wrap(~Metabolite, nrow = 2) +
  labs(y = expression("nmol / 10"^"6"~"cells")) +
  scale_y_continuous(trans = "log10") +
  theme_classic(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_signif(comparisons = list(c("WT", "KO"), c("WT", "IDKO")), test = "t.test", map_signif_level = TRUE, step_increase = 0.1, tip_length = 0.01)
```


### FA metabolism
```{r fa_initial_plots, fig.width = 14, fig.height= 18}
FA$Genotype <- factor(FA$Genotype, levels = c("WT", "KO", "IDKO"))
FA <- filter(FA, nmol_10Mcells != "NQ")
FA$nmol_10Mcells <- as.numeric(FA$nmol_10Mcells)

ggplot(FA, aes(Genotype, nmol_10Mcells)) +
  geom_boxplot(aes(fill = Genotype)) +
  facet_wrap(~Metabolite, nrow = 3) +
  labs(y = expression("nmol / 10"^"6"~"cells")) +
  scale_y_continuous(trans = "log10") +
  theme_classic(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        strip.text = element_text(size = 7)) +
  geom_signif(comparisons = list(c("WT", "KO"), c("WT", "IDKO")), test = "t.test", map_signif_level = TRUE, step_increase = 0.1, tip_length = 0.01)
```


### 'Other' metabolism
```{r other_initial_plots, fig.width = 12, fig.height= 18}
other$Genotype <- factor(other$Genotype, levels = c("WT", "KO", "IDKO"))

ggplot(other, aes(Genotype, nmol_10Mcells)) +
  geom_boxplot(aes(fill = Genotype)) +
  facet_wrap(~Metabolite, nrow = 3) +
  labs(y = expression("nmol / 10"^"6"~"cells")) +
  scale_y_continuous(trans = "log10") +
  theme_classic(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 9)) +
  geom_signif(comparisons = list(c("WT", "KO"), c("WT", "IDKO")), test = "t.test", map_signif_level = TRUE, step_increase = 0.1, tip_length = 0.01)
```



### PO4 metabolism
```{r po4_initial_plots, fig.width = 12}
PO4$Genotype <- factor(PO4$Genotype, levels = c("WT", "KO", "IDKO"))

ggplot(PO4, aes(Genotype, nmol_10Mcells)) +
  geom_boxplot(aes(fill = Genotype)) +
  facet_wrap(~Metabolite, nrow = 1) +
  labs(y = expression("nmol / 10"^"6"~"cells")) +
  scale_y_continuous(trans = "log10") +
  theme_classic(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_signif(comparisons = list(c("WT", "KO"), c("WT", "IDKO")), test = "t.test", map_signif_level = TRUE, step_increase = 0.1, tip_length = 0.01)
```



